---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eyetrackingElabR

<!-- badges: start -->
<!-- badges: end -->

The goal of eyetrackingElabR is to provide functions for basic processing 
of eye tracking data. 
The package is designed to support a variety of eye tracking data sources (but
was primarily tested using data exports from Tobii Studio and Tobii Pro). 


## Installation
*NOTE: this will not work until the package is published on github.com*
You can install the development version of eyetrackingElabR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("elab-umn/eyetrackingELabR")
```

## Package Documentation
To access package documentation and a list of all functions run 
``` r
help(package = "eyetrackingELabR")
```



## Contributing
1. Clone github repo
1. Open the eyetrackingElabR.Rproj file to launch the project in RStudio
1. Create a new branch (use the button on the "Git" pane in RStudio or use 
git commands in the Terminal)
1. Write code
1. Add tests using testthat package (see [tests/README](/tests/README.md))
1. Add documentation using roxygen (see [R package roxygen instructions](https://r-pkgs.org/man.html))
1. Once your changes are ready to be merged, submit a [pull request](https://docs.github.com/en/pull-requests/collaborating-with-pull-requests/proposing-changes-to-your-work-with-pull-requests/creating-a-pull-request) on github

If you find any bugs or have feature requests, [open an issue on github](https://github.com/elab-umn/eyetrackingELabR/issues). 
Please be as detailed as possible in your issue.

## Output Variable Data Dictionary
```{r dataDict, echo = FALSE}
library(knitr)

#Basic recording information definitions
recording_Variables <- c("event", "eventValue", "recordingDuration_ms", 
                         "resolutionHeight", "resolutionWidth", "eyeTrackerTimestamp",
                         "recordingTimestamp_ms")
recording_Definitions <- c("Stimulus event label", "Stimulus event value", "Total recording duration (ms)",
                           "Recording screen resolution height (px)", "Recording screen resolution width (px)",
                           "Internal eye tracker timestamp (unit?)", "Recording timecourse timestamp (ms)")

recording_Table <- data.frame(recording_Variables, recording_Definitions)
kable(recording_Table, col.names = c("Recording Information Variables", "Definitions"))

#GazePoint Definitions
GP_Variables <- c("gazeLeftX", "gazeLeftY", "gazeRightX","gazeRightY",
"gazeLeftX.int", "gazeLeftY.int", "gazeRightX.int", "gazeRightY.int",
"gazeX.eyeSelect", "gazeY.eyeSelect", "gazeX.smooth", "gazeY.smooth",
"gazeX.va","gazeY.va",
"gazeX.preprocessed_px", "gazeY.preprocessed_px",
"gazeX.preprocessed_va", "gazeY.preprocessed_va")
GP_Definitions <- c("Raw left eye X gaze position in pixels",
"Raw left eye Y gaze position in pixels",
"Raw right eye X gaze position in pixels",
"Raw right eye Y gaze position in pixels",
"Left eye X gaze position in pixels after interpolation",
"Left eye Y gaze position in pixels after interpolation",
"Right eye X gaze position in pixels after interpolation",
"Right eye Y gaze position in pixels after interpolation",
"Composite X gaze position after interpolation and eye selection",
"Composite Y gaze position after interpolation and eye selection",
"Composite X gaze position after interpolation, eye selection, and smoothing",
"Composite Y gaze position after interpolation, eye selection, and smoothing",
"X gaze position in visual angles",
"Y gaze position in visual angles",
"FINAL PREPROCESSED GAZE X POSITION IN PIXEL SPACE",
"FINAL PREPROCESSED GAZE Y POSITION IN PIXEL SPACE",
"FINAL PREPROCESSED GAZE X POSITION IN VISUAL ANGLE SPACE",
"FINAL PREPROCESSED GAZE Y POSITIONN IN VISUAL ANGLE SPACE")

GP_Table <- data.frame(GP_Variables, GP_Definitions)
kable(GP_Table, col.names = c("Gaze Position Variables", "Definitions"))

##Z distance table
Z_Variables <- c("distanceLeftZ", "distanceRightZ", "distanceLeftZ.int","distanceRightZ.int",
"distanceZ.eyeSelect", "distanceZ.smooth", "distanceZ.preprocessed_mm")
Z_Definitions <- c("Raw left eye Z position (distance from screen in mm)",
"Raw right eye Z position (distance from screen in mm)",
"Left eye Z position (distance from screen in mm) after interpolation",
"Right eye Z position (distance from screen in mm) after interpolation",
"Composite eye Z position (distance from screen) after interpolation and eye selection",
"Composite eye Z position (distance from screen) after interpolation, eye selection, and smoothing",
"FINAL PREPROCESSED Z DISTANCE POSITION IN MM")

Z_Table <- data.frame(Z_Variables, Z_Definitions)
kable(Z_Table, col.names = c("Z Distance Variables", "Definitions"))

#Velocity Definitions
Vel_Variables <- c("velocityX_va_ms", "velocityY_va_ms", "velocityEuclidean_va_ms",
"velocityX.smooth_va_ms", "velocityY.smooth_va_ms", "velocityEuclidean.smooth_va_ms",
"velocityX.preprocessed_va_ms", "velocityY.preprocessed_va_ms", "velocityEuclidean.preprocessed_va_ms")
Vel_Definitions <- c(
"X gaze velocity in VA/second (lagged by two gazepoints)",
"Y gaze velocity in VA/second (lagged by two gazepoints)",
"Euclidean velocity in VA/second (lagged by two gazepoints)",
"X gaze velocity in VA/second after smoothing",
"Y gaze velocity in VA/second after smoothing",
"Euclidean velocity in VA / second after smoothing",
"FINAL PREPROCESSED X GAZE VELOCITY IN VA/SECOND",
"FINAL PREPROCESSED Y GAZE VELOCITY IN VA/SECOND",
"FINAL PREPROCESSED EUCIDEAN VELOCITY IN VA/SECOND")

Vel_Table <- data.frame(Vel_Variables, Vel_Definitions)
kable(Vel_Table, col.names = c("Velocity Variables", "Definitions"))

#IVT Definitions
IVT_Variables <- c("IVT.classification", "IVT.fixationIndex", "IVT.saccadeIndex","IVT.fixationDuration_ms")
IVT_Definitions <- c("FINAL IVT FILTER CLASSIFICATION", 
  "Index number of fixation",
  "Index number of saccade",
  "Total duration of fixation (ms)")
IVT_Table <- data.frame(IVT_Variables, IVT_Definitions)
kable(IVT_Table, col.names = c("IVT Variables", "Definitions"))

#Validity Definitions
validity_Variables <- c("validLeft", "validRight", "gazeLeft.offscreen", "gazeRight.offscreen",
                        "offscreen.classification")
  
validity_Definitions <- c("Input for classifying left eye validity", "Input for classigying right eye validity",
                          "Classification of left eye offscreen gaze validity", "Classification of right eye offscreen gaze validity",
                          "FINAL CLASSIFICATION OF OVERALL OFFSCREEN VALIDITY")

validity_Table <- data.frame(validity_Variables, validity_Definitions)
kable(validity_Table, col.names = c("Validity Variables", "Definitions"))

#Pupil Definitions
Pupil_Variables <- c("pupilLeft", "pupilRight", "pupilLeft.int",
"pupilRight.int", "pupil.eyeSelect", "pupil.smooth", "pupil.preprocessed",
"pupilLeft.blink", "pupilRight.blink", "bothEyes.blink", "blink.classification")
Pupil_Definitions <- c(
"Raw left pupil data",
"Raw right pupil data",
"Interpolated left pupil data",
"Interpolated right pupil data",
"Pupil data after interpolation and eye selection",
"Pupil data after interpolation, eye selection, and smoothing",
"FINAL PREPROCESSED PUPIL DATA",
"Flags blinks in left eye (where 1 = blink)",
"Flags blinks in right eye (where 1 = blink)",
"Flags where blinks occur concurrently in both left and right eyes",
"FINAL BLINK CLASSIFICATION (based on eyeSelection method)")
Pupil_Table <- data.frame(Pupil_Variables, Pupil_Definitions)
kable(Pupil_Table, col.names = c("Pupil and Blink Variables", "Definitions"))
```
